On optimisation in HDR brachytherapy

### 2015-03-07 Paper BMT/article-sample-proceedings.tex
added parts of PL results

\subsection{Results}
bla bla bla
unsure bla bla
\section{Stepwise Approach}
The use of Linear Programming for HDR brachytherapy treatment planning is extended to a stepwise approach as described in \citep{3}.

>>>>

\subsection{Results}
As shown in tabel \ref{table:LP_results50} and \ref{table:LP_results100}, the relaxation of the PTV increases the conformality, while letting the coverage of the PTV drop. 
		\begin{table}[h]
			\centering		
		 	\caption{LP 50 seeds}
		 	\label{table:LP_results50}
			\begin{tabular}{ccc}
			PTV lower bound [Gy] 	& Coverage 	& Conformality Index\\	\hline
				32.0 	& 0.999		& 1.23\\
				31.0 	& 0.988 	& 1.20\\
				30.0 	& 0.953		& 1.17\\		
				29.0 	& 0.899		& 1.14\\
			\end{tabular}
		\end{table}

Using more initial seeds, the algorithm can achieve higher conformality without losing coverage.

				\begin{table}[h]
			\centering		
		 	\caption{LP 100 seeds}
		 	\label{table:LP_results100}
			\begin{tabular}{ccc}
			PTV lower bound [Gy] 	& Coverage 	& Conformality Index\\	\hline
				32.0 	& 0.999		& 1.16\\
				31.0 	& 0.981 	& 1.13\\
				30.0 	& 0.931		& 1.10\\		
				29.0 	& 0.851		& 1.08\\
			\end{tabular}
		\end{table}

mehr tabellen bla. ahh ohh vergleich

\section{Stepwise Approach}
The use of Linear Programming for HDR brachytherapy treatment planning is extended to a stepwise approach as described in \citep{3}.
